\section{Work domains}
We have identified two primary work domains: Course creation and Doctors practice.

\subsection{Course creation}
\subsubsection{Definition}
The course creation work domain is the source that DMA uses to provide material for their members to educate themselves. It is not limited to the creators that DMA are directly linked with, but also external third party creators.

\subsubsection{Characterization}
DMA has multiple sources of courses and material of differing types and they are delivered in different ways, from BMJ’s e-learning platform, DMA’s own courses and courses created elsewhere and communicated to members through and by DMA.

The sources have different delivery methods, course content, evaluation methods and purpose.

DMA primarily uses their website and other IT based channels to inform their members of the existence of these courses, and to some extent also give access to them.

\subsubsection{Discussion/conclusion}
The constraints and methods in course creation are key to determining what is possible to actually do in terms of innovative ideas.

\subsection{Doctors practice}
\subsubsection{Definition}
The actual work practice and daily schedule of DMA’s members, the doctors, and how much time and resources they have available for learning new things. This means both considering the day to day work schedule and any time dedicated to learning.

\subsubsection{Characterization}
Although DMA serves a very diverse member group, there is some common ground and work practices among a large part of their members. The doctors have a busy working day that is not very flexible, making it difficult for them to make time for the current format of provided courses.

Additionally some members lack incentive to prioritise learning over working, as some doctors are paid to learn, others are not.

\subsubsection{Discussion/conclusion}
Whatever the quality of the courses provided by DMA may be, the doctors have to be able to find the time to take them. The courses also need to cater for the actual interests of the doctors and be relevant in their daily work.

